Quick example of a simple QC plot for a LC-MS/MS run
========================================================

QC of proteomics data is often neglected many published studies or internal projects. This is unfortunate as the overall thesis will be shaky at the best if due dilligent is not observed.

The summary data was generated from an LC-MS/MS analysis using another program written in Java. It collects many useful statistics as the function of peptide retention time.

```{r}
  library(lattice)
  thro = read.csv(stringsAsFactors=F, row.names=NULL, "/home/wyu/Projects/R/data/sputum_thro_59881.csv")
```

The content of the summary stats is shown below.
```{r fig.width=7, fig.height=6}
  head(thro)
```

```{r}
  # remove the row col
  thro$row=NULL
  # convert the columns
  thro$id.run = as.factor(unique(thro$id.run))
  thro$id.prj = as.factor(unique(thro$id.prj))
  thro$id.expt = as.factor(unique(thro$id.expt))
  thro$rt.pct = as.numeric(thro$rt.pct)
  thro$rt     = as.numeric(thro$rt)
  thro$width  = as.numeric(thro$width)
  thro$val    = as.numeric(thro$val)
  thro$annot  = as.logical(thro$annot)  

  junk = subset(thro, slice=="mw"&annot==TRUE&stat=="apex")
```

As an example, we can plot the MS1 intensities (apex) verus RT

```{r fig.width=7, fig.height=6}
  xyplot(val~rt.pct|name, data=junk, type=c("p","l"), scales="free")
```

